---
output:
  html_document:
    df_print: paged
  always_allow_html: yes
---

# Loading packages

```{r,echo=TRUE, warning=FALSE, message=FALSE}
#setwd("~/R")
library(knitr)
library(ggplot2)
library(Hmisc)
library(kableExtra)
library(dplyr)
#library(gmodels)
library(emmeans)
#library(funModeling)
library(funModeling)
library(skimr)
library(janitor)
library(corrr)
library(corrplot)
library(tidyverse)
library(caret)
library(PerformanceAnalytics)
library(AICcmodavg)
library(visreg)
library(performance)

```

```{r,echo=TRUE, warning=FALSE, message=FALSE}
data<- read.csv("stacking.csv", header = TRUE, sep =",")
data<-data.frame(data)
data$week = as.numeric(data$week)
data$hurrier_orders = as.numeric(data$hurrier_orders)
data$hurrier_opd = as.numeric(data$hurrier_opd)
data$unique_active_rider = as.numeric(data$unique_active_rider)
data$reordered = as.numeric(data$reordered)
data$churn = as.numeric(data$churn)
data<-cbind(data,per_rider_weekly_income_eur = data$total_rider_earning_eur/data$unique_active_rider)
#View(data)
rmarkdown::paged_table(head(data))
#summary(data)

```

```{r,echo=TRUE, warning=FALSE, message=FALSE}
data_x<-data.frame(data$hurrier_orders,data$hurrier_opd,data$unique_active_rider,data$dt,data$delayed_order_perc,data$rider_late,data$vendor_late,data$rider_fill_rate_perc,data$utr_overall,data$stacked_deliveries_perc,data$weighted_surge_time_perc,data$weighted_shrinkage_time_perc,data$ao_nps,data$csat_perc,data$seamless_order_perc,data$auto_comp_cpo,data$comp_cpo,data$refund_comp_cpo,data$total_rider_earning_eur,data$rider_cpo,data$rider_cph,data$reordered,data$reordered_7day_perc,data$churn)

```

## Normalizing the dataframe

```{r,echo=TRUE, warning=FALSE, message=FALSE}
preProcess(data)
chart.Correlation(data[,c(3,5,6,7,8,9,10,11,13,33,35,40)], histogram=TRUE, pch=19)
```

```{r,echo=TRUE, warning=FALSE, message=FALSE}

flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
mdata_x<-(as.matrix(data_x))

mdata_x <- rcorr(as.matrix(data_x))
#mdata_X
```

```{r,echo=TRUE, warning=FALSE, message=FALSE}
y<-flattenCorrMatrix(mdata_x$r, mdata_x$P)
#print(y)
rmarkdown::paged_table((y))
```

#r : The table of correlation coefficients. #p : Table of p-values corresponding to the significance levels of the correlations. #sym : A representation of the correlation matrix in which coefficients are replaced by symbols according to the strength of the dependence.

# Plots

```{r,echo=TRUE, warning=FALSE, message=FALSE}

g0<-data %>%
     ggplot(aes(x = stacked_deliveries_perc, y =dt
                , colour=week)) +
     geom_point(size=2) +
    geom_smooth(se=F, colour="grey")
plot(g0)


g1<- data %>%
     ggplot(aes(x = stacked_deliveries_perc, y = comp_cpo, colour=week)) +
     geom_point(size=2) +
    geom_smooth(se=F, colour="grey")
plot(g1)

g2<-data %>%
     ggplot(aes(x = stacked_deliveries_perc, y = refund_comp_cpo, colour=week)) +
     geom_point(size=2) +
    geom_smooth(se=F, colour="grey")
plot(g2)
g3<-data %>%
     ggplot(aes(x = stacked_deliveries_perc*100, y = rider_cpo
                , colour=week)) +
     geom_point(size=2) +
    geom_smooth(se=F, colour="grey")
plot(g3)

g4<- data %>% ggplot(aes(x = stacked_deliveries_perc, y = auto_comp_cpo, colour=week)) +geom_point(size=2) + geom_smooth(se=F, colour="grey")
plot(g4)

```

#### Modeling

```{r,echo=TRUE, warning=FALSE, message=FALSE}
options(scipen=999)
m1<- lm(dt ~ log(delayed_order_perc) + log(rider_fill_rate_perc) + utr_overall + daily_working_hours + p_d_distance_km + log(stacked_deliveries_perc) + log(single_stacked_deliveries_perc) + log(double_stacked_deliveries_perc) +
log(triple_stacked_deliveries_perc) + churn + log(weighted_surge_time_perc) + log(weighted_shrinkage_time_perc), data = data)
summary(m1)
#plot(m1)
#visreg(m1)
ggplot(data,aes(x= stacked_deliveries_perc, y= dt)) + geom_point() + geom_smooth(method= "lm")


```

### Model Prediction - (DELIVERY TIME)

#### Taking the following assumption from historical data as the status_quo:

-   order_per_rider_day = 4.5
-   unique_active_rider = 12000
-   p_d\_distance_km = 1.4
-   dt = 27
-   delayed_order_perc = 35%
-   delayed_above_10_mins_perc = 12%
-   rider_late = -5.5
-   vendor_late = 4.2
-   rider_fill_rate_perc = 87%
-   utr_overall = 1.5
-   daily_working_hours = 42000
-   stacked_deliveries_perc = 24%
-   single_stacked_deliveries_perc = 20% (total_stack : single_stack = 1.2:1)
-   double_stacked_deliveries_perc = 4% (single_stack : double_stack = 5:1)
-   triple_stacked_deliveries_perc = 0.8% (double_stack : triple_stack = 5:1)
-   weighted_shrinkage_time_perc = 5%
-   weighted_surge_time_perc = 20%
-   ao_nps = -4.0
-   csat_perc = 55%
-   reordered_perc = 78%
-   reordered_7day_perc = 55%
-   reordered_30_day_perc = 70%
-   churn = 1800
-   total_rider_earning_eur = 162786994.6

```{r, echo=TRUE, warning = FALSE, message = FALSE}
pred_dt<-as.data.frame(cbind(week= data$week,actual_dt= data$dt, predict_dt= predict(m1)))
rmarkdown::paged_table(pred_dt)

## When things are normal and stacking ~24%:
dt_pred1= predict(m1,data.frame(delayed_order_perc = 0.35,rider_fill_rate_perc = 0.87,utr_overall= 1.5,p_d_distance_km=1.4, daily_working_hours =42000, stacked_deliveries_perc = 0.24, single_stacked_deliveries_perc =0.20, double_stacked_deliveries_perc =0.04, triple_stacked_deliveries_perc=0.008, churn=1800, weighted_surge_time_perc=0.30, weighted_shrinkage_time_perc =0.10), interval ="confidence")
print(dt_pred1)

# When stacking is increased by 5%% 
dt_pred2= predict(m1,data.frame(delayed_order_perc = 0.35,rider_fill_rate_perc = 0.87,utr_overall= 1.5,p_d_distance_km=1.4, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.05, single_stacked_deliveries_perc = 0.20+0.04, double_stacked_deliveries_perc =0.04+0.008 , triple_stacked_deliveries_perc=0.008+0.0016, churn=1800, weighted_surge_time_perc=0.30, weighted_shrinkage_time_perc =0.10), interval ="confidence")
print(dt_pred2)

# When stacking is increased by 10% 
dt_pred3= predict(m1,data.frame(delayed_order_perc = 0.35,rider_fill_rate_perc = 0.87,utr_overall= 1.5,p_d_distance_km=1.4, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.10, single_stacked_deliveries_perc = 0.20+0.08, double_stacked_deliveries_perc =0.04+0.016 , triple_stacked_deliveries_perc=0.008+0.0032, churn=1800, weighted_surge_time_perc=0.30, weighted_shrinkage_time_perc =0.10), interval ="confidence")
print(dt_pred3)

# When stacking is increased by 15% 
dt_pred4= predict(m1,data.frame(delayed_order_perc = 0.35,rider_fill_rate_perc = 0.87,utr_overall= 1.5,p_d_distance_km=1.4, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.15, single_stacked_deliveries_perc = 0.20+0.125, double_stacked_deliveries_perc =0.04+0.025 , triple_stacked_deliveries_perc=0.008+0.005, churn=1800, weighted_surge_time_perc=0.30, weighted_shrinkage_time_perc =0.10), interval ="confidence")
print(dt_pred4)

# When stacking is decreased by 5% 
dt_pred5= predict(m1,data.frame(delayed_order_perc = 0.35,rider_fill_rate_perc = 0.87,utr_overall= 1.5,p_d_distance_km=1.4, daily_working_hours =42000, stacked_deliveries_perc = 0.24-0.05, single_stacked_deliveries_perc = 0.20-0.04, double_stacked_deliveries_perc =0.04-0.008 , triple_stacked_deliveries_perc=0.008-0.0016, churn=1800, weighted_surge_time_perc=0.30, weighted_shrinkage_time_perc =0.10), interval ="confidence")
print(dt_pred5)

```

### Model Prediction - (RIDER CPO)

```{r,echo=TRUE, warning=FALSE, message=FALSE}
m2<- lm(rider_cpo ~ order_per_rider_per_day + unique_active_rider + utr_overall + per_rider_weekly_income_eur + daily_working_hours + p_d_distance_km + log(stacked_deliveries_perc) + log(single_stacked_deliveries_perc) + log(double_stacked_deliveries_perc) +
log(triple_stacked_deliveries_perc) + churn, data = data)
summary(m2)

#predict(m2, newdata= st)
#plot(m2)
#visreg(m2)

ggplot(data,aes(x= stacked_deliveries_perc, y= rider_cpo)) + geom_point() + geom_smooth(method= "lm")

```

```{r,echo=TRUE, warning=FALSE, message=FALSE}
pred_rider_cpo<-as.data.frame(cbind(week= data$week,actual_rider_cpo= data$rider_cpo, pred_rider_cpo= predict(m2)))
rmarkdown::paged_table(pred_rider_cpo)

## When things are normal and stacking ~24%:
pred_rider_cpo1= predict(m2,data.frame(order_per_rider_per_day = 4.5, per_rider_weekly_income_eur = 14.1, unique_active_rider= 12000,utr_overall= 1.5,p_d_distance_km=1.4, daily_working_hours =42000, stacked_deliveries_perc = 0.24, single_stacked_deliveries_perc =0.20, double_stacked_deliveries_perc =0.04, triple_stacked_deliveries_perc=0.008, churn=1800), interval ="confidence")
print(pred_rider_cpo1)

# When stacking is increased by 5%% 
pred_rider_cpo2= predict(m2,data.frame(order_per_rider_per_day = 4.5, utr_overall= 1.5, per_rider_weekly_income_eur = 14.1, unique_active_rider=12000, p_d_distance_km=1.4, total_rider_earning_eur= 162786994.6, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.05, single_stacked_deliveries_perc = 0.20+0.04, double_stacked_deliveries_perc =0.04+0.008 , triple_stacked_deliveries_perc=0.008+0.0016, churn=1800), interval ="confidence")
print(pred_rider_cpo2)

# When stacking is increased by 10% 
pred_rider_cpo3= predict(m2,data.frame(order_per_rider_per_day = 4.5, utr_overall= 1.5, unique_active_rider= 12000, per_rider_weekly_income_eur = 14.1, p_d_distance_km=1.4, total_rider_earning_eur= 162786994.6, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.10, single_stacked_deliveries_perc = 0.20+0.08, double_stacked_deliveries_perc =0.04+0.016 , triple_stacked_deliveries_perc=0.008+0.0032, churn=1800), interval ="confidence")
print(pred_rider_cpo3)

# When stacking is increased by 15% 
pred_rider_cpo4= predict(m2,data.frame(order_per_rider_per_day = 4.5,utr_overall= 1.5, unique_active_rider= 12000, per_rider_weekly_income_eur = 14.1,p_d_distance_km=1.4, daily_working_hours =42000,total_rider_earning_eur= 162786994.6, stacked_deliveries_perc = 0.24+0.15, single_stacked_deliveries_perc = 0.20+0.125, double_stacked_deliveries_perc =0.04+0.025 , triple_stacked_deliveries_perc=0.008+0.005, churn=1800), interval ="confidence")
print(pred_rider_cpo4)

# When stacking is decreased by 5% 
pred_rider_cpo5= predict(m2,data.frame(order_per_rider_per_day = 4.5,utr_overall= 1.5,p_d_distance_km=1.4, unique_active_rider=12000, per_rider_weekly_income_eur = 14.1, total_rider_earning_eur= 162786994.6, daily_working_hours =42000, stacked_deliveries_perc = 0.24-0.05, single_stacked_deliveries_perc = 0.20-0.04, double_stacked_deliveries_perc =0.04-0.008 , triple_stacked_deliveries_perc=0.008-0.0016, churn=1800), interval ="confidence")
print(pred_rider_cpo5)

rbind(pred_rider_cpo1,pred_rider_cpo2,pred_rider_cpo3,pred_rider_cpo4,pred_rider_cpo5)

```

### Model Prediction - (AUTO COMPENSATION CPO)

```{r,echo=TRUE, warning=FALSE, message=FALSE}

m3<- lm(auto_comp_cpo ~ dt + log(delayed_order_perc) + daily_working_hours  + log(stacked_deliveries_perc) + log(single_stacked_deliveries_perc) + log(double_stacked_deliveries_perc) +
log(triple_stacked_deliveries_perc) + log(reordered_perc+0.00001) + log(reordered_7day_perc+0.00001) + log(reordered_30_day_perc+0.00001) + log(csat_perc) + ao_nps, data = data)
summary(m3)
plot(m3)
#visreg(m3)
ggplot(data,aes(x= stacked_deliveries_perc, y= auto_comp_cpo)) + geom_point() + geom_smooth(method= "lm")

```

```{r,echo=TRUE, warning=FALSE, message=FALSE}

pred_auto_comp_cpo<-as.data.frame(cbind(week= data$week,actual_auto_comp_cpo= data$auto_comp_cpo, pred_auto_comp_cpo= predict(m3)))
rmarkdown::paged_table(pred_auto_comp_cpo)

## When things are normal and stacking ~24%:
pred_auto_comp_cpo1= predict(m3,data.frame(dt=27,delayed_order_perc =0.35, daily_working_hours =42000, stacked_deliveries_perc = 0.24, single_stacked_deliveries_perc =0.20, double_stacked_deliveries_perc =0.04, triple_stacked_deliveries_perc=0.008, reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70, csat_perc=0.55 ,ao_nps= -4.0), interval ="confidence")
print(pred_auto_comp_cpo1)

# When stacking is increased by 5%% 
pred_auto_comp_cpo2= predict(m3,data.frame(dt=27,delayed_order_perc= 0.35, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.05, single_stacked_deliveries_perc = 0.20+0.04, double_stacked_deliveries_perc =0.04+0.008 , triple_stacked_deliveries_perc=0.008+0.0016, reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70, csat_perc=0.55 ,ao_nps= -4.0), interval ="confidence")
print(pred_auto_comp_cpo2)

# When stacking is increased by 10% 
pred_auto_comp_cpo3= predict(m3,data.frame(dt=27,delayed_order_perc= 0.35, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.10, single_stacked_deliveries_perc = 0.20+0.08, double_stacked_deliveries_perc =0.04+0.016 , triple_stacked_deliveries_perc=0.008+0.0032,reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70, csat_perc=0.55 ,ao_nps= -4.0 ), interval ="confidence")
print(pred_auto_comp_cpo3)

# When stacking is increased by 15% 
pred_auto_comp_cpo4= predict(m3,data.frame(dt=27,delayed_order_perc= 0.35, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.15, single_stacked_deliveries_perc = 0.20+0.125, double_stacked_deliveries_perc =0.04+0.025 , triple_stacked_deliveries_perc=0.008+0.005,reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70, csat_perc=0.55 ,ao_nps= -4.0), interval ="confidence")
print(pred_auto_comp_cpo4)

# When stacking is decreased by 5% 
pred_auto_comp_cpo5= predict(m3,data.frame(dt=27,delayed_order_perc= 0.35,daily_working_hours =42000, stacked_deliveries_perc = 0.24-0.05, single_stacked_deliveries_perc = 0.20-0.04, double_stacked_deliveries_perc =0.04-0.008 , triple_stacked_deliveries_perc=0.008-0.0016,reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70, csat_perc=0.55 ,ao_nps= -4.0 ), interval ="confidence")
print(pred_rider_cpo5)


rbind(pred_auto_comp_cpo1,pred_auto_comp_cpo2,pred_auto_comp_cpo3,pred_auto_comp_cpo4,pred_auto_comp_cpo5)


```

### Model Prediction - (REFUND COMPENSATION CPO)

```{r,echo=TRUE, warning=FALSE, message=FALSE}
m4<- lm(refund_comp_cpo ~ dt + log(delayed_order_perc) + utr_overall + daily_working_hours + log(stacked_deliveries_perc) + log(single_stacked_deliveries_perc) + log(double_stacked_deliveries_perc) +
log(triple_stacked_deliveries_perc) + log(reordered_perc+0.00001) + log(reordered_7day_perc+0.00001) + log(reordered_30_day_perc+0.00001), data = data)
summary(m4)
plot(m4)
#visreg(m4)
ggplot(data,aes(x=stacked_deliveries_perc, y= refund_comp_cpo)) + geom_point() + geom_smooth(method= "lm")
```

```{r,echo=TRUE, warning=FALSE, message=FALSE}
pred_refund_comp_cpo<-as.data.frame(cbind(week= data$week,actual_refund_comp_cpo= data$refund_comp_cpo, pred_refund_comp_cpo= predict(m4)))
rmarkdown::paged_table(pred_refund_comp_cpo)

## When things are normal and stacking ~24%:
pred_refund_comp_cpo1= predict(m4,data.frame(dt=27,delayed_order_perc =0.35, utr_overall= 1.5,daily_working_hours =42000, stacked_deliveries_perc = 0.24, single_stacked_deliveries_perc =0.20, double_stacked_deliveries_perc =0.04, triple_stacked_deliveries_perc=0.008, reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70), interval ="confidence")
print(pred_refund_comp_cpo1)

# When stacking is increased by 5%% 
pred_refund_comp_cpo2= predict(m4,data.frame(dt=27,delayed_order_perc= 0.35,utr_overall= 1.5, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.05, single_stacked_deliveries_perc = 0.20+0.04, double_stacked_deliveries_perc =0.04+0.008 , triple_stacked_deliveries_perc=0.008+0.0016, reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70), interval ="confidence")
print(pred_refund_comp_cpo2)

# When stacking is increased by 10% 
pred_refund_comp_cpo3= predict(m4,data.frame(dt=27,delayed_order_perc= 0.35,utr_overall= 1.5, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.10, single_stacked_deliveries_perc = 0.20+0.08, double_stacked_deliveries_perc =0.04+0.016 , triple_stacked_deliveries_perc=0.008+0.0032,reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70), interval ="confidence")
print(pred_refund_comp_cpo3)

# When stacking is increased by 15% 
pred_refund_comp_cpo4= predict(m4,data.frame(dt=27,delayed_order_perc= 0.35,utr_overall= 1.5, daily_working_hours =42000, stacked_deliveries_perc = 0.24+0.15, single_stacked_deliveries_perc = 0.20+0.125, double_stacked_deliveries_perc =0.04+0.025 , triple_stacked_deliveries_perc=0.008+0.005,reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70), interval ="confidence")
print(pred_refund_comp_cpo4)

# When stacking is decreased by 5% 
pred_refund_comp_cpo5= predict(m4,data.frame(dt=27,delayed_order_perc= 0.35,utr_overall= 1.5,daily_working_hours =42000, stacked_deliveries_perc = 0.24-0.05, single_stacked_deliveries_perc = 0.20-0.04, double_stacked_deliveries_perc =0.04-0.008 , triple_stacked_deliveries_perc=0.008-0.0016,reordered_perc=0.78, reordered_7day_perc = 0.55,reordered_30_day_perc=0.70), interval ="confidence")
print(pred_refund_comp_cpo5)


rbind(pred_refund_comp_cpo1,pred_refund_comp_cpo2,pred_refund_comp_cpo3,pred_refund_comp_cpo4,pred_refund_comp_cpo5)
```
